Flow-Directed Trace Analysis for Post-Silicon Validation

### 2015-08-23 paper.tex
k
number changed

After the SoC model finishes executing the program, there are totally $343581$ messages collected in the trace file.  Not all of the messages are relevant to the flow specification as many are used by GEM5 to initialize its simulation environment.  After removing those irrelevant messages, the number of messages in the trace file is to reduced to $120949$.

The time taken to remove the irrelevant messages from the trace is negligible.  The total runtime and the peak memory usage for the trace analysis algorithm to finish the reduced trace are 3 seconds and 12MB, respectively.  From the trace, Table~\ref{table-case-2} shows the number of instances extracted for the four flows describing cache coherent read/write operations. 
\begin{table}[td]
\caption{The number of flow instances derived by the trace analysis}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Flows & $\#$Instances \\
\hline
\hline
CPU1 Read		&  $21584$\\
CPU1 Write	&  $3370$\\
CPU2 Read		&  $21341$\\
CPU2 Write	&  $3308$\\
\hline
\end{tabular}
\end{center}
\label{table-case-2}
\end{table}%

>>>>

After the SoC model finishes executing the program, there are totally $343581$ messages collected in the trace file.  Not all of the messages are relevant to the flow specification as many are used by GEM5 to initialize its simulation environment.  After removing those irrelevant messages, the number of messages in the trace file is to reduced to $121138$.

The time taken to remove the irrelevant messages from the trace is negligible.  The total runtime and the peak memory usage for the trace analysis algorithm to finish the reduced trace are 3 seconds and 12MB, respectively.  From the trace, Table~\ref{table-case-2} shows the number of instances extracted for the four flows describing cache coherent read/write operations. 
\begin{table}[td]
\caption{The number of flow instances derived by the trace analysis}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Flows & $\#$Instances \\
\hline
\hline
CPU1 Read		&  $4002$\\
CPU1 Write	&  $3370$\\
CPU1 Failed Read  &$95$\\
CPU2 Read		&  $3955$\\
CPU2 Write	&  $3308$\\
CPU2 Failed Read  &$93$\\
\hline
\end{tabular}
\end{center}
\label{table-case-2}
\end{table}%
